resistanceModelNotesAndy

### 2016-04-28 paper1_results_figs.Rmd
testing that mix always slower than sole

  #****************
  #not sure I need to do this because all results already show mixture better
  #now I want to subset just those runs where start freq old is > 10 * new

@@

>>>>

  #not sure I need to do this because all results already show mixture better
  #now I want to subset just those runs where start freq old is > 10 * new

@@

  #28/4/16 testing Ians statement
  #does resistance always arise faster in sole use than in a mixture (irrespective of starting frequencies)
  #resistPointsI1_T #"insecticide 1" 
  #resistPointsI2_T #"insecticide 2"
  #resistPointsMixI1_T #"I1inMix" 
  #resistPointsMixI2_T #"I2inMix"

  mix_minus_soleI1 <- resistPointsMixI1_T["gen_cP0.5"] - resistPointsI1_T["gen_cP0.5"]
  which( mix_minus_soleI1 < 0 ) 
  #0
  mix_minus_soleI2 <- resistPointsMixI2_T["gen_cP0.5"] - resistPointsI2_T["gen_cP0.5"]
  which( mix_minus_soleI2 < 0 ) 
  #0

  #so yes in our param space adding an extra insecticide always increases resistance time for the first

  #i could plot it against exposure & effectiveness
